Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-09 manuscript/climate_sensitivity_draft.Rmd
update model description in text to GLMM
#94

Analyses focused on testing the predictions presented in Table 1, with $Rt$ as the response variable. The general statistical model for hypothesis testing was a mixed effects model with $Rt$ as the response variable, tree nested within species as a random effect, and one or more independent variables as fixed effects. Mixed effects models were implemented in the lme4 package in R [@R-lme4]. We used AICc to assess model selection, and conditional/marginal R-squared to assess model fit as implmented in the AICcmodavg package in R [@R-AICcmodavg]. AICc refers to a corrected version of AICc, and is best suited for small data sizes [see @brewer_relative_2016]

@@

We then determined the best full models for predicting $Rt$ for each individual drought year and for all years combined. Candidate variables were selected, based on the single-variable tests, as those that had a consistent direction of response across all droughts and whose addition to a corresponding null model improved fit (at $\Delta$AICc $\ge$ 1.0) in at least one drought year (Table 4). We note that the $\Delta$AICc $\ge$ 1.0 criterion is not a test of signficance, but of whether the variable has enough influence to be considered as a *candidate* variable in full models. We compared models with all possible combinations of candidate variables and identified the full set of models within $\Delta$AICc=1 of the very top model (that with lowest AICc), henceforth referred to as "full models". When a variable appeared in all top models and the sign of the coefficient was consistent across models, we viewed this as support for the acceptance/rejection of the associated prediction by the full models. If the variable appeared in only some of the models, we considered this partial support/rejection.

>>>>

Analyses focused on testing the predictions presented in Table 1, with $Rt$ as the response variable. The general statistical model for hypothesis testing was a generalized linear mixed model with $Rt$ as the response variable, tree nested within species as a random effect, and one or more independent variables as fixed effects. Generalized linear mixed models were implemented in the **XX** package in R [**REF**]. We used AICc to assess model selection, and conditional/marginal R-squared to assess model fit as implemented in the AICcmodavg package in R [@R-AICcmodavg]. AICc refers to a corrected version of AICc, and is best suited for small data sizes [see @brewer_relative_2016]

@@

We then determined the best full models for predicting $Rt$ for each individual drought year and for all years combined. Candidate variables were selected, based on the single-variable tests, as those that had a consistent direction of response across all droughts and whose addition to a corresponding null model improved fit (at $\Delta$AICc $\ge$ 1.0) in at least one drought year (Table 4). We note that the $\Delta$AICc $\ge$ 1.0 criterion is not a test of significance, but of whether the variable has enough influence to be considered as a *candidate* variable in full models. We compared models with all possible combinations of candidate variables and identified the full set of models within $\Delta$AICc=1 of the very top model (that with lowest AICc), henceforth referred to as "full models". When a variable appeared in all top models and the sign of the coefficient was consistent across models, we viewed this as support for the acceptance/rejection of the associated prediction by the full models. If the variable appeared in only some of the models, we considered this partial support/rejection.
